Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-11 02_Paper/paper.tex
Conclusions

It is important to state that this prediction model is not yet ready to fully replace the statistical methods, not the hundred percent quality check method, since this research is still on its early stages and need further development. However, a combination of SPC along prediction models could work well together, since the prediction model will evaluate each produced piece, and this might compensate one disadvantage of the statistical methods.

>>>>

It is important to state that this prediction model is not yet ready to fully replace the statistical methods, nor the hundred percent quality check method, since this research is still in its early stages and needs further development. However, a combination of SPC along prediction models could work well together, since the prediction model will evaluate each produced piece, and this might compensate for disadvantages of the statistical methods.
